Perceptions and Preferences for Meritocracy

### 2020-04-22 docs/paper.Rmd

The proposed scale of perceptions and preferences about meritocracy consists of 8 indicators that are grouped into the 4 dimensions indicated. The questions are adaptations of the "get ahead" scale. the terms of of this scale were used (i.e talent, effort, contacts and wealthy parents) which are included in different investigations on meritocracy [@mijs_paradox_2019; @duru-bellat_whos_2012; @reynolds_perceptions_2014]. Unlike this scale, this proposal adds the difference between perceptions and preferences. In addition, a comparative component is incorporated into the question that refers to differences between people with little or fed up with some attribute (e.g. effort, contacts).The eight items ordered according to dimensions are presented in Table 2. These 8 likert-type items have 5 response alternatives ranging from "I completely agree" (5) to "I completely disagree"(1). According to the recommendations of Xia and Yang ([2018](https://link.springer.com/article/10.3758/s13428-018-1055-2)) for categorical data, we present below a table with the descriptive table and another with correlations between the items on the scale.

>>>>

The proposed scale of perceptions and preferences about meritocracy consists of 8 indicators that are grouped into the 4 dimensions indicated. The questions are adaptations of the "get ahead" scale. the terms of of this scale were used (i.e talent, effort, contacts and wealthy parents) which are included in different investigations on meritocracy [@mijs_paradox_2019; @duru-bellat_whos_2012; @reynolds_perceptions_2014]. Unlike this scale, this proposal adds the difference between perceptions and preferences. In addition, a comparative component is incorporated into the question that refers to differences between people with little or fed up with some attribute (e.g. effort, contacts).The eight items ordered according to dimensions are presented in Table 2. These 8 likert-type items have 5 response alternatives ranging from "I completely agree" (5) to "I completely disagree"(1). According to the recommendations of Xia and Yang ([2018](https://link.springer.com/article/10.3758/s13428-018-1055-2)) for categorical data, we present below a table with the descriptive table and another with correlations between the items on the scale.
=======
The field work was conducted during November and December of 2019 in Chile, obtaining a final sample of 2200 individuals, but considering that we use cases with complete information, the final analytical sample has 2141 observations.

<!-- [Descriptive Table for the PPM-S, by group or the full sample] -->

```{r echo=FALSE}
load(file = "output/tables/sumdat04.RData");sumdat04
```
